Schramm-Loewner evolution in tricritical Ising model

### 2013-06-24 AffineLieAlgebras/Simons/paper.tex
Paper outlined

@@

\section{Statement of the main theorem}
\label{sec:results}

\section{RSOS realization of the Ising and tricritical Ising model}
\label{sec:rsos-real-ising}

>>>>

\newtheorem{theorem}{Theorem}

@@

\subsection{Statement of the main theorem}
\label{sec:results}

\begin{theorem}
  For tricritical Ising model on upper half plane there exists s-holomorphic observable $f$ given by the
  formula. It satisfies discrete boundary problem with boundary conditions. In the limit it
  converges to analytic function. Correlation function of something $F$ can be calculated as $F=f+if$.
\end{theorem}
\section{RSOS realization of the Ising and tricritical Ising model}
\label{sec:rsos-real-ising}

Tricritical Ising model was introduced as a modification of the Ising model \cite{}. The model is
the dilute Ising model with the Hamiltonian 
\begin{equation}
  \label{eq:1}
  H = -\beta \sum_{<i,j>}\sigma_i\sigma_j - \mu \sum_{i}(\sigma_i)^2.
\end{equation}
Here $\mu$ is chemical potential of vacancies,
if $\mu$ tends to zero we recover ordinary Ising model without vacant sites. We consider the model on some domain
$\Omega$ in complex plane. The model has three vacuum states with the spins on all sites equal to
$+1$, $-1$ and $0$. In tricritical point the vacuum is degenerate.

(Phase diagram here)

(In tricritical point this model is conformally-invariant and described by CFT)

There is another lattice model in the same universality class. It is $A_4$ Restricted Solid-on-Solid
(RSOS) model.

In restricted solid-on-solid models spins on the sites take values labeled by the
nodes of simply-laced Dynkin diagram. The values at the adjacent sites must be adjacent on the
Dynkin diagram.

The weight of the configuration $C$ is equal to the product of
face weights and boundary weights:
\begin{equation}
  \label{eq:7}
  W(c)=\prod_{f\in \mathrm{faces}} W(f,C) \prod_{b\in \mbox{\small{boundary
      faces}}} B(b,C)
\end{equation}

Face weight is determined by the Perron-Frobenius
eigenvector $\psi$ of the adjacency matrix $G$ of Dynkin diagram. Denote by $2\cos\lambda$ be the
highest eigenvalue of $G$, then $\sum_{b\in {\cal G}} G_{ab}\psi_b = 2\cos(\lambda) \psi_a $ and 
by the Perron-Frobenius theorem $\psi_a \neq 0$.

Bolzmann weight for a face with vertex labels $a,b,c,d$ is given by the formula
\begin{equation}
  \label{eq:5}
    W\left.\left(
    \begin{array}{cc}
      d & c\\
      a & b
    \end{array}\right| u \right)
= s_1 (-u)\delta_{ac} + \frac{s_0 (u) \psi_a^{1/2}
  \psi_c^{1/2}}{\psi_b} \delta_{bd},
\end{equation}
where
  \begin{equation}
    \label{eq:6}
    s_r(u)=\frac{\sin(r\lambda+u)}{\sin\lambda},\quad \frac{\lambda}{\pi}\not\in\mathbb{Z}.
  \end{equation}

Bulk weights satisfy Yang-Baxter equation \cite{behrend2001integrable}
that leads to integrability of the model using transfer matrix
approach.

Bolzmann weights for the lattice edges can differ from face weights.
Choice of these weights corresponds to different boundary conditions.
Conformally invariant boundary conditions for $A_4$ RSOS realization
of the tricritical Ising model were identified in
\cite{chim1996boundary}, boundary weights were listed in
\cite{behrend2001integrable}.

Behrend and Pearce use following labeling of boundary conditions for
rank $g$ model:
$\left\{(r,a)\ |\ r\in\{1,\dots,g-1\}, a\in {\cal G}\right\}$. For the
$(1,a)$ boundary condition boundary weights are given by the equation
\begin{equation}
  \label{eq:8}
  B^{1,a}\left.\left( c
    \begin{array}{ll}
      a & 1\\
      a & 1
    \end{array}\right| u, \xi \right)= \frac{s_0(\xi+u) s_1(\xi-u)
  \psi^{1/2}_c } {s_0(2\xi) \psi_a^{1/2}}
\end{equation}

So in the $(1, a)$ boundary condition the state of every alternate
boundary spin is fixed to be $a$, while each other boundary spin,
with state $c$ adjacent to $a$ on ${\cal G}$, is associated with a
weight proportional to $\psi_c^{1/2}$.

These boundary weights satisfy the boundary Yang-Baxter equation.

%%%%%%%%%%
For the Ising and tricritical Ising models we limit ourselves with $r=1$
boundary states. 
%%%%%%%%%%

Ising model is realized using $A_{3}$ diagram. If we enumerate the nodes by $1,2,3$ the sites with
values $1$ and $3$ correspond to positive and negative spins and the sublattice with $2$-s is frozen
and do not play any role.

For RSOS realization of Ising model we have:
\begin{eqnarray}
  \label{eq:10}
  2 \cos\lambda = \sqrt{2}\\
  \lambda=\frac{\pi}{4}\\
  \psi = (1,\sqrt{2},1)
\end{eqnarray}
Values on even sublattice sites are fixed to $2$ and odd sublattice
values $1,3$ can be mapped to Ising spins $-1,+1$. Critical value for
Ising model is $K_C=\frac{1}{2}\log (1+\sqrt{2})$.

So we obtain Boltzmann weights:
\begin{equation}
  \label{eq:9}
  \begin{array}{lllll}
    V_{-} &=& W\left.\left(
    \begin{array}{ll}
      2 & 3\\
      1 & 2
    \end{array}\right| u \right) &=&   W\left.\left(
    \begin{array}{ll}
      2 & 1\\
      3 & 2
    \end{array}\right| u
\right)=\frac{1}{\sqrt{2}} \frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
H_{-}&=&W\left.\left(
    \begin{array}{ll}
      1 & 2\\
      2 & 3
    \end{array}\right| u\right) &=&  W\left.\left(
    \begin{array}{ll}
      3 & 2\\
      2 & 1
    \end{array}\right| u
\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\

V_{+}&=&W\left.\left(
    \begin{array}{ll}
      2 & 1\\
      1 & 2
    \end{array}\right| u
\right)&=&   W\left.\left(
    \begin{array}{ll}
      2 & 3\\
      3 & 2
    \end{array}\right| u
\right)= \frac{\sin\left( u\right) }{\sqrt{2}\,\sin\left(
    \lambda\right) }-\frac{\sin\left( u-\lambda\right) }{\sin\left(
    l\right) } = \sin(u)-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
H_{+}&=&W\left.\left(
    \begin{array}{ll}
      1 & 2\\
      2 & 1
    \end{array}\right| u
\right)&=&   W\left.\left(
    \begin{array}{ll}
      3 & 2\\
      2 & 3
    \end{array}\right| u
\right)= \frac{\sqrt{2}\sin\left( u\right) }{\sin\left(
    \lambda\right) }-\frac{\sin\left( u-\lambda\right) }{\sin\left(
    l\right) } = 2\sin(u)-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)
\end{array}
\end{equation}
Here we have denoted by $V_{\pm}, H_{\pm}$ Boltzmann weights for
vertical and horizontal adjacent spins with positive ($+$) or negative
($-$) product. The case $u=\lambda/2=\frac{\pi}{8}$ is isotropic
$\frac{V_+}{V_-}=\frac{H_+}{H_-}= 1+\sqrt{2}=e^{2 K_C}$.

%% The crucial object in the proof of convergence of lattice correlations
%% to correlation functions in critical limit is parafermionic observable
%% of Smirnov, Hongler \cite{1202.2838v2}.
%% 
%% It can be defined as follows: consider Ising configuration on a double cover of domain $\Omega$
%% with singularity at $z$. 
%%

  We are interested in the case $A_4$, so we have
$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
The isotropic case $u=\lambda/2$ with boundary parameters
$u=\xi_1=\xi_2=\lambda/2$ corresponds to the  conformal point. Then we have
$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.

\begin{itemize}
\item Boltzmann weights for $A_{4}$
\item Boundary weights ?
\item Critical point, isotropicity
\item Loop description (two types of loops, duality, similarity with dilute Ising model) 
\end{itemize}
